## R Notebook and rCharts for NY Times 512 Paths to the White House

This is a short demo on recreating the **NY Times** interactive feauture [512 Paths to the White House](http://www.nytimes.com/interactive/2012/11/02/us/politics/paths-to-the-white-house.html?_r=0) in an R Markdown notebook, using rCharts and Shiny. If you want to follow along, please install `rCharts` from `github` using `devtools`.

```{r eval = F}
require(devtools)
install_github('rCharts', 'ramnathv')
```

Before we begin charting, let us customize some settings for rCharts and knitr as copied from [the example.Rmd included with rCharts](https://github.com/ramnathv/rCharts/tree/master/inst/apps/notebook/www).

```{r echo = T, message = F, cache = F}
require(rCharts)
options(RCHART_WIDTH = 600, RCHART_HEIGHT = 400)
knitr::opts_chunk$set(comment = NA, results = 'asis', tidy = F, message = F)
```


---
```{r}
#get data from downloaded NYT tsv and inject in through params
data <- read.delim(file = "http://timelyportfolio.github.io/rCharts_512paths/data/states.tsv")

#quick look at the data
require(xtable)
print( xtable( head( data ) ), type = "html" )

#let's randomize the order a bit and make some states more powerful
#data[,-5] <- data[order( runif( n=nrow( data ) ) ),-5]
#print( xtable( head( data ) ), type = "html" )

#now let's deliberately change some data
print( xtable( head( data[which(data$code == "FL"), ] ) ), type = "html" )
#data[which(data$code == "FL"),"votes"] <- 10
#data[which(data$code == "FL"),"rep"] <- 0.9
#data[which(data$code == "FL"),"dem"] <- 1 - data[which(data$code == "FL"),"rep"]
#print( xtable( head( data[which(data$code == "FL"), ] ) ), type = "html" )
#print( xtable( head( data[which(data$code == "OH"), ] ) ), type = "html" )
#data[which(data$code == "OH"),"votes"] <- 0

p1 <- rCharts$new()
p1$field( 'lib', "/assets/x512paths" )
p1$set( data = toJSONArray( data ) )
p1$print( 'g-chart' )
```
---

## Additional Credit from me
Thanks [Ramnath](http://github.com/ramnathv) for rCharts and slidify.

## Credits in Original Example

I would like to acknowledge the efforts of @yihui and @rstudio in bringing R Notebooks to the R community. I would like to thank @yihui for his excellent shiny app in the knitr package, which was the basis for this app. Without their efforts, rCharts and this demo would not have been possible.

For more information, check out

http://github.com/ramnathv/rCharts
