# R Notebook with rCharts
<h2 style="color:rgb(148, 190, 163);text-align:center"> NY Times 512 Paths to the White House</h2>
<br/>
### Introduction and Setup
This is a short demo on recreating the **NY Times** interactive feauture [512 Paths to the White House](http://www.nytimes.com/interactive/2012/11/02/us/politics/paths-to-the-white-house.html?_r=0) in an R Markdown notebook, using rCharts and Shiny. If you want to follow along, please install `rCharts` from `github` using `devtools`.  To see the original tutorial, go [here](http://timelyportfolio.github.io/rCharts_512paths).

```{r eval = F}
require(devtools)
install_github('rCharts', 'ramnathv')
```

Before we begin charting, let us customize some settings for rCharts and knitr as copied from [the example.Rmd included with rCharts](https://github.com/ramnathv/rCharts/tree/master/inst/apps/notebook/www).

```{r echo = T, message = F, cache = F}
require(rCharts)
options(RCHART_WIDTH = 600, RCHART_HEIGHT = 400)
knitr::opts_chunk$set(comment = NA, results = 'asis', tidy = F, message = F)
```


---
### Build the Chart & Then Play What If?
```{r}
#get data from downloaded NYT tsv and inject in through params
data <- read.delim(file = "http://timelyportfolio.github.io/rCharts_512paths/data/states.tsv")

#quick look at the data
require(xtable)

options(
  xtable.html.table.attributes = 
    'class="table table-condensed table-bordered table-striped"'
)
print( xtable( head( data ) ), type = "html" )

#cat("<h4>let's randomize the order a bit and make some states more powerful</h4>")
#data$votes <- data$votes[order( runif( n = nrow( data ) ) )]
#print( xtable( head( data ) ), type = "html" )

#now let's deliberately change some data
#print( xtable( head( data[which(data$code == "FL"), ] ) ), type = "html" )
#data[which(data$code == "FL"),"votes"] <- 10
#data[which(data$code == "FL"),"rep"] <- 0.9
#data[which(data$code == "FL"),"dem"] <- 1 - data[which(data$code == "FL"),"rep"]
#print( xtable( head( data[which(data$code == "FL"), ] ) ), type = "html" )
#print( xtable( head( data[which(data$code == "OH"), ] ) ), type = "html" )
#data[which(data$code == "OH"),"votes"] <- 0

p1 <- rCharts$new()
p1$field( 'lib', "www/assets/x512paths" )
p1$set( data = toJSONArray( data ) )
p1$print( 'g-chart' )
```
---

### Credits in Original Example

>I would like to acknowledge the efforts of @yihui and @rstudio in bringing R Notebooks to the R community. I would like to thank @yihui for his excellent shiny app in the knitr package, which was the basis for this app. Without their efforts, rCharts and this demo would not have been possible.

### Additional Credit from me
Thanks [Ramnath](http://github.com/ramnathv) for rCharts and slidify and genius bug elimination.


<br/>
For more information, check out

http://github.com/ramnathv/rCharts
